Was simultaneous marathon finish in Rio coincidental?

### 2017-01-29 paper/paper.tex
update

\subsection*{Simulate the run}

\begin{enumerate}
\item Removing the twins from the sample, estimate a linear model that
predicts a runner?s final time (y) based on her personal best time (x).
\item Extract the coefficients and the variance-covariance matrix from this
model.
\item For each runner, draw $\beta_0$ and $\beta_1$ from a multivariate normal
distribution with mean equal to the coefficients and variance equal to the
variance-covariance matrix.
\item For each runner, draw an error term ($e$) from a normal distribution with
mean equal to zero and a standard deviation equal to the standard
deviation of the model?s residuals.
\item For each runner, predict the final result by combining the randomly
generated beta coefficients and error terms, $\hat{y} = \beta_0 + \beta_1 + e$.
\item Eliminate each runner from the race with a probability equal to the
percent of the total runners who did not finish in the actual race.  This
account for the likelihood of a DNF.
\item Calculate the runner?s rank relative to the other runners.
\item From the rankings, determine if each set of twins finished
consecutively.
\item Repeat steps 2 through 8 ten thousand times.
\item Calculate the percent of the simulation in which the twins finished
consecutively
\end{enumerate}

\begin{figure}[!ht]
 \caption{The distribution of simulated results}
 \label{fig:diffdiff}
 \begin{subfigure}{.5\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{simulated_time.pdf}
 \end{subfigure}
 \begin{subfigure}{.5\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{simulated_rank.pdf}
 \end{subfigure}
\end{figure}

>>>>

\newpage
\subsection*{Steps of the simulation}

\begin{enumerate}
\item Removing the twins from the sample, estimate a linear model that
predicts a runner?s final time ($Y_i$) based on her personal best time ($X_i$).
\item Extract the coefficients and the variance-covariance matrix from this
model.
\item For each runner, draw $\beta_0$ and $\beta_1$ from a multivariate normal
distribution with mean equal to the coefficients and variance equal to the
variance-covariance matrix.
\item For each runner, draw an error term ($e$) from a normal distribution with
mean equal to zero and a standard deviation equal to the standard
deviation of the model?s residuals ($\sigma$).
\item For each runner, predict the final result by combining the randomly
generated beta coefficients and error terms, $\hat{y} = \beta_0 + \beta_1 + e$.
\item Eliminate each runner from the race with a probability equal to the
percent of the total runners who did not finish in the actual race.  This
account for the likelihood of a DNF.
\item Calculate the difference in time between Anna Hahner and Lisa Hahner.
\item Calculate the difference in ranking between Anna Hahner and Lisa Hahner.
\item Repeat steps 3 through 8 ten thousand times.
\item Plot a histogram of the results in Figure \ref{fig:simdiff}
\end{enumerate}

\begin{figure}[!ht]
 \caption{The distribution of simulated results}
 \label{fig:simdiff}
 \begin{subfigure}{.5\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{simulated_time.pdf}
 \end{subfigure}
 \begin{subfigure}{.5\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{simulated_rank.pdf}
 \end{subfigure}
\end{figure}
